Modeling Macroeconomic Phenomena \\with Multi-Agent Reinforcement Learning

### 2019-12-06 paper/paper.tex
Added information + captions about actor critic

\subsection{RL Algorithms******}
Both the learning algorithms chosen for the simulation were policy gradient methods. This was chosen due to previous literature, and because such methods have stronger convergence guarantees than value-based reinforcement learning methods (though potentially to non-global optima).

@@

\begin{figure}[h]
\begin{tikzpicture}[every mark/.append style={mark size=1pt}]
  \begin{axis}[
    xlabel=Episode,
    ylabel=Policy Loss,
    legend style={at={(1,0)}, anchor=south east}
  ]
  \addplot table [y=pl, x=i]{a2c.dat};
  \addlegendentry{Firm}
  \end{axis}
\end{tikzpicture}
\caption{Policy Network Loss in Actor Critic Method}
\label{plt:a2cpolicyloss}
\end{figure}

\begin{figure}[h]
\begin{tikzpicture}[every mark/.append style={mark size=1pt}]
  \begin{axis}[
    xlabel=Episode,
    ylabel=Critic Loss,
    legend style={at={(1,0)}, anchor=south east}
  ]
  \addplot table [y=al, x=i]{a2c.dat};
  \addlegendentry{Firm}
  \end{axis}
\end{tikzpicture}
\caption{Critic Network Loss in Actor Critic Method}
\label{plt:a2cadvloss}
\end{figure}

>>>>

\subsection{RL Algorithms}
Both the learning algorithms chosen for the simulation were policy gradient methods. This was chosen due to previous literature, and because such methods have stronger convergence guarantees than value-based reinforcement learning methods (though potentially to non-global optima).

@@

We also attempted to run both Q Actor-Critic and A2C algorithms for the firm in the same monopoly situation as before (one firm with five people). However, while the policy networks would consistently converge (see Figure \ref{plt:acpolicyloss}), the critic networks would rarely converge, about 10\% of the time (see Figure \ref{plt:acadvloss}). For this reason, we chose to stick with REINFORCE as the reinforcement learning model for future simulations.

\begin{figure}[h]
\begin{tikzpicture}[every mark/.append style={mark size=1pt}]
  \begin{axis}[
    xlabel=Episode,
    ylabel=Policy Loss,
    legend style={at={(1,0)}, anchor=south east}
  ]
  \addplot table [y=pl, x=i]{a2c.dat};
  \addlegendentry{Firm}
  \end{axis}
\end{tikzpicture}
\caption{Policy Network Loss in Q Actor Critic Method: with one actor-critic firm agent and five human agents, the firm's policy network loss converges rather quickly to 0 (note that the y-axis increments are rather small). Like in REINFORCE, when the policy becomes close to deterministic, the loss approaches zero.}
\label{plt:acpolicyloss}
\end{figure}

\begin{figure}[h]
\begin{tikzpicture}[every mark/.append style={mark size=1pt}]
  \begin{axis}[
    xlabel=Episode,
    ylabel=Critic Loss,
    legend style={at={(1,0)}, anchor=south east}
  ]
  \addplot table [y=al, x=i]{a2c.dat};
  \addlegendentry{Firm}
  \end{axis}
\end{tikzpicture}
\caption{Critic Network Loss in Q Actor Critic Method: with one actor-critic firm agent and five human agents, the firm's critic loss does not converge, even with changing the learning rate. This was also true when we used A2C, which is supposed to address variance issues with a baseline. Note that the scale on the y-axis is quite large.}
\label{plt:acadvloss}
\end{figure}
